\Title

### 2021-01-19 manuscript/manuscript.tex
Add github repository url
Start writing the conclusions

>>>>

Equivalent sources that uses the inverse of the distance as the Green's
functions are well suited for interpolating gravity disturbance data.
Block-averaged sources reduces the number of point sources, reducing the
computational load needed to estimate their coefficients, preventing aliasing
on the interpolated values while maintaining accurate predictions.
Special attention must be payed when choosing the size of the block spacing:
as a thumb rule, it must be approximately equal to the resolution of the
regular grid where the values will be interpolated.
The three compared strategies for setting the depth of the sources (constant
depth, relative depth and variable depth) don't significantly affect
the accuracy of the interpolations.
Nevertheless, the choice of the parameters for each depth strategy does affects
the accuracy and the frequency components of the interpolations.

Gradient-boosted equivalent sources heavily reduces the computer memory
needed to estimate source coefficients, making possible to interpolate even
very large datasets.
The interpolations obtained though this new method achieve almost the same
accuracy than the non-boosted sources, while reducing the computation time
needed to estimate the source coefficients.
Because it doesn't involve any assumption on the location of the sources, it
can be used in conjunction with any horizontal source layout and any strategy
for setting their depth.
Moreover, the results equivalent sources can be used not only for interpolating
on a regular grid, but also on any set of observation points, allowing to
create profiles or upward continuations.
In order to maximize the accuracy of the interpolations, the size of the
rolling windows must be chosen as the maximum value that creates Jacobian
matrices that fit into our computer memory.
Therefore its choice is subject to the particular infrastructure where the
interpolation will be carried out.
We have shown that an overlap of 50\% between adjacent windows achieves a good
compromise between accuracy and computation time needed to fit the source
coefficients.

The gradient-boosted equivalent sources were used to interpolate a compilation
of more than 1.7 million gravity points from Australia on a regular grid with
a resolution of 1~arc-minute.
The whole process was carried out on a modest personal computer, requiring
a maximum of 10GB of memory.
This shows how the new gradient-boosted equivalent sources can be applied to
real-world data.
